---
title: "phaRmacy"
author: "Chris Beeley"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

```{r, include=FALSE}

drug <- pharmacy %>% 
  filter(NSVCode == drug_code) %>% 
  filter(Site1 == x) %>%
  filter(Total_Qty >= 0) %>% 
  group_by(Date) %>%
  summarise(quantity = sum(Total_Qty, na.rm = TRUE)) %>% 
  ungroup() %>%  
  tsibble(index = Date) %>% 
  fill_gaps(quantity = 0)

drug_week <- pharmacy %>% 
  filter(NSVCode == drug_code) %>% 
  filter(Site1 == x) %>%
  filter(Total_Qty >= 0) %>% 
  mutate(Date = floor_date(Date, "week"),
         Date = yearweek(Date)) %>%
  group_by(Date) %>%
  summarise(quantity = sum(Total_Qty, na.rm = TRUE)) %>% 
  ungroup() %>% 
  head(-1) %>% # remove the last row in case it isn't a complete week
  tsibble(index = Date) %>% 
  fill_gaps(quantity = 0)

# horizon for prediction 6 weeks

h <- 6

```

#### `r x`

##### Seasonality

###### Week

```{r}

drug %>% 
  gg_subseries(period = "week")

```

###### Year

```{r, fig.height=10}

drug_year <- drug %>% 
  mutate(year = year(Date))

year(drug_year$Date) = 2020

drug_year %>% 
  ggplot(aes(x = Date, y = quantity)) + 
  geom_line() +
  facet_wrap(~ year, ncol = 1)

drug_week %>% 
  gg_season(quantity, "year")

```

###### Raw data

```{r}

drug %>%
  model(STL(quantity ~ trend(window = 11) + season(c("1 week", "1 year")),
            robust = TRUE)) %>%
  components() %>%
  autoplot() + 
  ggtitle("Raw data STL decomposition")

```

###### Detail of data

```{r}

drug %>%
  model(STL(quantity ~ trend(window = 11) + season(c("1 week", "1 year")),
            robust = TRUE)) %>%
  components() %>%
  tail(365 * 2) %>% 
  autoplot() + 
  ggtitle("Raw data STL decomposition")

```

###### Weekly totals

```{r}

drug_week %>%
  model(STL(quantity ~ trend(window = 11) + season("1 year"),
            robust = TRUE)) %>%
  components() %>%
  autoplot() + 
  ggtitle("Weekly totals STL decomposition")

```

###### Detail of weekly totals

```{r}

drug_week %>%
  model(STL(quantity ~ trend(window = 11) + season(c("1 week", "1 year")),
            robust = TRUE)) %>%
  components() %>%
  tail(52 * 2) %>% 
  autoplot() + 
  ggtitle("Weekly totals STL decomposition")

```

##### Residuals of STL model- raw data and weekly totals

```{r}

# compare residuals

bind_rows(
  drug %>%
    model(STL(quantity ~ trend(window = 11) + season(c("1 week", "1 year")),
              robust = TRUE)) %>%
    components() %>% 
    as_tibble() %>% 
    mutate(model = "raw") %>% 
    select(model, remainder),
  
  drug_week %>%
    model(STL(quantity ~ trend(window = 11) + season(c("1 week", "1 year")),
              robust = TRUE)) %>%
    components() %>% 
    as_tibble() %>% 
    mutate(model = "weekly") %>% 
    select(model, remainder)
) %>% 
  ggplot(aes(x = remainder)) + geom_histogram() + 
  facet_wrap(~ model, scales = "free")

```

##### Simple exponential smoothing

```{r}

fit_ets <- drug_week %>% 
  model(ETS(quantity ~ season(method = "N")))

fit_ets %>% 
  sw_tidy() %>% 
  kable()

fit_ets %>% 
  gg_tsresiduals(lag_max = 16)

```

Ljung Box test for autocorrelation of residuals

```{r}

augment(fit_ets) %>%
  features(.resid, ljung_box, lag = 16, dof = 6) %>% 
  kable()

```

##### ARIMA

```{r}

arima_drug <- drug_week %>% 
  model(ARIMA(quantity))

arima_drug %>% 
  sw_tidy() %>% 
  kable()

gg_tsresiduals(arima_drug, lag_max = 16)

arima_drug %>% 
  augment() %>% 
  autoplot(.resid)

```

Ljung Box test for autocorrelation of residuals

```{r}

arima_drug %>%
  augment() %>% 
  features(.resid, ljung_box, lag = 16, dof = 6) %>% 
  kable()

```

##### Model testing

###### Weekly data

```{r}

drug_train <- drug_week %>% 
  head(-h)

drug_model <- drug_train %>% 
  model(SNAIVE(quantity), 
        ARIMA(quantity),
        ETS(quantity ~ season(method = "N")),
        prophet(quantity)) %>% 
  forecast(h = h)

drug_model %>% 
  autoplot(drug_week %>% tail(h), level = NULL)

drug_model %>% 
  accuracy(drug_week) %>% 
  mutate(across(where(is.numeric), signif, 5)) %>%
  select(-ACF1) %>%
  kable()

```

###### Daily data

```{r}

drug_train <- drug %>% 
  head(-42)

drug_model_day <- drug_train %>% 
  model(SNAIVE(quantity), 
        ARIMA(quantity),
        ETS(quantity ~ season(method = "N")),
        prophet(quantity)) %>% 
  forecast(h = 42)

drug_model_day %>% 
  autoplot(drug %>% tail(42), level = NULL)

drug_model_day %>% 
  accuracy(drug) %>% 
  mutate(across(where(is.numeric), signif, 5)) %>%
  select(-ACF1) %>%
  kable()

```

##### Cross validation

Cross validated accuracy for a variety of models using weekly data.

```{r}

drug_week_cv <- drug_week %>%
  slice(1 : (n() - 1)) %>%
  stretch_tsibble(.init = 10, .step = 10)

cv_model <- drug_week_cv %>%
  model(ETS(quantity ~ season(method = "N")),
        SNAIVE(quantity), 
        ARIMA(quantity),
        prophet(quantity)) %>% 
  forecast(h = 1)

cv_model %>% 
  accuracy(drug_week) %>% 
  kable()
  

```

###### Cross validation- daily

Cross validated accuracy for a variety of models using daily data.

```{r}

drug_day_cv <- drug %>%
  slice(1 : (n() - 1)) %>%
  stretch_tsibble(.init = 10, .step = 200)

cv_model_day <- drug_day_cv %>%
  model(ETS(quantity ~ season('N')),
        SNAIVE(quantity), 
        ARIMA(quantity),
        prophet(quantity)) %>% 
  forecast(h = 1)

cv_model_day %>% 
  accuracy(drug) %>% 
  kable()

```
