---
title: "Summary of Drug A"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(lubridate)
library(fable)
library(tibbletime)
library(feasts)
library(tsibble)
library(sweep)
library(knitr)
library(fable.prophet)
library(pander)
library(fasster)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = TRUE, results = "asis")

load("pharmacy.rda")

# forecast horizon

h <- 42

```

## Summary of numbers

```{r}

pharmacy %>% 
  filter(NSVCode == "Drug A") %>% 
  filter(Total_Qty >= 0) %>% 
  group_by(Site1) %>%
  summarise(quantity = sum(Total_Qty, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(daily_average = quantity / as.numeric((max(pharmacy$Date) - min(pharmacy$Date)))) %>% 
  pandoc.table()

```

## Predict Site C

```{r}

site_c <- pharmacy %>% 
  filter(NSVCode == "Drug A") %>% 
  filter(Site1 == "Site C") %>%
  filter(Total_Qty >= 0) %>% 
  group_by(Date) %>%
  summarise(quantity = sum(Total_Qty, na.rm = TRUE)) %>% 
  ungroup() %>%  
  tsibble(index = Date) %>% 
  fill_gaps(quantity = 0)

train_c <- site_c %>% 
  head(-h)

model_c <- train_c %>% 
  model(SNAIVE(quantity ~ lag("week")), 
        ARIMA(quantity),
        ETS(quantity ~ season(method = "A")),
        prophet(quantity ~ season(7)),
        FASSTER(quantity ~ trend(1) + fourier(7))) %>% 
  forecast(h = h)

model_c %>% 
  bind_rows(site_c %>% 
              tail(h) %>% 
              rename(.mean = quantity) %>% 
              mutate(.model = "Actual")) %>% 
  ggplot(aes(x = Date, y = .mean, 
             group = .model, colour = .model)) + 
  geom_line() + facet_wrap( ~ .model)

# model_c %>% 
#   autoplot(site_c %>% tail(h), level = NULL)

model_c %>% 
  accuracy(site_c) %>% 
  mutate(across(where(is.numeric), signif, 5)) %>%
  select(-ACF1) %>%
  kable()

```

## Cross validation

```{r}

site_c_cv <- site_c %>%
  slice(1 : (n() - 42)) %>%
  slide_tsibble(.size = 1000, .step = 200)

cv_model <- site_c_cv %>%
  model(SNAIVE(quantity ~ lag("week")), 
        ARIMA(quantity),
        ETS(quantity ~ season(method = "A")),
        prophet(quantity ~ season(7)),  
        FASSTER(quantity ~ trend(1) + fourier(7))) %>%
  forecast(h = h)

cv_accuracy <- cv_model %>% 
  group_by(.model, .id) %>% 
  ungroup() %>% 
  accuracy(site_c)

cv_accuracy %>% 
  arrange(.model) %>% 
  select(.model, RMSE, MAE, ACF1) %>% 
  pandoc.table()

```

Cross validation results are considerably better, indicating that the most recent results, presumably by chance, conform less to the model.

ETS is the best model, giving around 330 mean average error compared with a daily average dispensed drug of 471.

## Predict Site B

```{r}

site_b <- pharmacy %>% 
  filter(NSVCode == "Drug A") %>% 
  filter(Site1 == "Site B") %>%
  filter(Total_Qty >= 0) %>% 
  group_by(Date) %>%
  summarise(quantity = sum(Total_Qty, na.rm = TRUE)) %>% 
  ungroup() %>%  
  tsibble(index = Date) %>% 
  fill_gaps(quantity = 0)

train_b <- site_b %>% 
  head(-h)

model_b <- train_b %>% 
  model(SNAIVE(quantity ~ lag("week")), 
        ARIMA(quantity),
        ETS(quantity ~ season(method = "A")),
        prophet(quantity ~ season(7)),
        FASSTER(quantity ~ trend(1) + fourier(7))) %>% 
  forecast(h = h)

model_b %>% 
  bind_rows(site_b %>% 
              tail(h) %>% 
              rename(.mean = quantity) %>% 
              mutate(.model = "Actual")) %>% 
  ggplot(aes(x = Date, y = .mean, 
             group = .model, colour = .model)) + 
  geom_line() + facet_wrap( ~ .model)

# model_b %>% 
#   autoplot(site_b %>% tail(h), level = NULL, facet = .model)

model_b %>% 
  accuracy(site_b) %>% 
  mutate(across(where(is.numeric), signif, 5)) %>%
  select(-ACF1) %>%
  kable()

```

## Cross validation

```{r}

site_b_cv <- site_b %>%
  slice(1 : (n() - 1)) %>%
  stretch_tsibble(.init = 200, .step = 200)

cv_model_b <- site_b_cv %>%
  model(SNAIVE(quantity ~ lag("week")), 
        ARIMA(quantity),
        ETS(quantity ~ season(method = "A")),
        prophet(quantity ~ season(7)),
        FASSTER(quantity ~ trend(1) + fourier(7))) %>% 
  forecast(h = h)

cv_model_b %>% 
  accuracy(site_c) %>% 
  kable()

```

Results are poor for site B, with the lowest mean average error (around 360 for prophet) higher than the daily average for this site (289).
